\section{User Story Quality Analysis Techniques}\label{usq}
In this section, we embark on an exposition of methodologies with the specific objective of refining the precision of User Stories measurement. First, in subsection \ref{us} the role of USs and backlogs in agile development will be discussed. Additionally, the most common pattern of US will be introduced.

From subsection \ref{invest} our focus centers on the exploration of established techniques to address the query regarding the existence of criteria for the management and identification of conflicts and dependencies among User Stories. Furthermore, our attention is directed towards the criteria they employ, a pivotal factor in ensuring the creation of well-structured and standardized User Stories. After this exploration, we undertake a comprehensive comparative analysis of these methodologies to ascertain the approach that best aligns with our particular contextual requirements.
\subsection{Role of User Stories and Backlogs in Agile Development} \label{us}
The agile software development paradigm broke the wall that classically existed between the development team and end-users. Thanks to the involvement of a Product Owner (PO) who acts as a proxy to end-users for the team, the product backlog \cite{sedano2019product} became a first-class citizen during the product development. Furthermore, thanks to a set of user stories expressing features to be implemented in the product in order to deliver value to end-users, the development teams were empowered to think in terms of added value when planning their subsequent developments. The product is then developed iteration by iteration, incrementally. Each iteration selects a subset of the stories, maintaining a link between the developers and the end-users\cite{mosser2022modelling}. 

\textbf{\emph{Ordinarily, User Stories typically exhibit interdependencies, wherein the order of their implementation becomes a critical consideration. This circumstance raises the question of how one may discern and identify the relationships that exist between the User Stories.}}

Sedano et al. posited that a “product backlog is an informal model of the work to be done” \cite{sedano2019product}. A backlog implements a shared mental model over practitioners working on a given product, acting as a boundary artifact between stakeholders. This model is voluntarily kept informal to support rapid prototyping and brainstorming sessions. Classically, backlogs are stored in project management systems, such as \footnote{\href{https://www.atlassian.com/en/software/jira}{Jira Software}} Jira. These tools store user stories as tickets, where stakeholders write text as natural language. Meta-data (e.g., architecture components, severity, quality attribute) can also be attached to the stories. However, there is no formal language to express stories or model backlogs from a state of practice point of view.

A user story is a brief, semi-structured sentence and informal description of some aspect of a software system that illustrates requirements from the user’s perspective \cite{raharjana2021user}. Large, vague stories are called epics. While user stories vary widely between organizations, most observed stories included a motivation and acceptance criteria. The brief motivation statement followed the pattern:  As a  \textless\emph{user}\textgreater\ I want to \textless\emph{action}\textgreater\ so that \textless\emph{value}\textgreater. This is sometimes called the Connextra template. The acceptance criteria followed the pattern: Given \textless\emph{context}\textgreater, when \textless\emph{condition}\textgreater \  then \textless\emph{action}\textgreater. This is sometimes called Gherkin syntax \cite{wynne2017cucumber}. It consists of three aspects, namely aspects of who, what and why. The aspect of “who” refers to the system user or actor, “what” refers to the actor’s desire, and “why” refers to the reason (optional in the user story) \cite{raharjana2021user}.

The user story components consist of the following elements \cite{wautelet2017user} : \emph{Role}: abstract behaviour of actors in the system context; the aspect of who representation. \emph{Goal}: a condition or a circumstance desired by stakeholders or actors. Task: specific things that must be done to achieve goals. \emph{Capability}: the ability of actors to achieve goals based on certain conditions and events.
\subsection{Improving User Story using INVEST Criteria} \label{invest}
In Agile software development, effective requirement management is crucial for delivering valuable and high-quality software. The INVEST criteria serve as a set of guiding principles that help teams assess and shape their user stories and requirements to meet the demands of Agile development. Each letter in the acronym INVEST represents a fundamental attribute that a requirement should possess to maximize its effectiveness within an Agile context.

These criteria were introduced to ensure that Agile teams create requirements that are not only clear and actionable but also adaptable to changing circumstances. The goal is to promote flexibility, collaboration, and a relentless focus on delivering value to the end-users or stakeholders \cite{buglione2013improving}.

In the following, we will examine the individual INVEST criteria in depth, with a focus on explaining their importance and their pragmatic application in the context of Agile Requirement Engineering \cite{cohn2004user}. \\ 
\textbf{Independent} \\ 
Independent emphasize the avoidance of interdependencies between user stories or requirements. This principle underscores the importance of ensuring that each requirement operates autonomously, without relying on the completion of other related requirements. The presence of dependencies among requirements can introduce complexities in the prioritization and planning phases of Agile development. Such dependencies may necessitate a specific order of implementation, hindering the team's ability to adapt to changing priorities and potentially causing delays in project delivery. \\ 
\textbf{Negotiable}\\ 
 USs (User Stories) should not be construed as rigid, contractual obligations or exhaustive lists of requirements that the software must adhere to. Instead, they are viewed as dynamic entities, open to ongoing discussion and refinement.

US are not meant to encapsulate every conceivable detail at the outset. The inclusion of excessive details can create a deceptive illusion of precision or completeness, potentially stifling the need for continued dialogue and collaboration. 

An essential attribute of negotiable USs are their inherent flexibility. It is crucial to avoid treating User Stories as contractual obligations, as this can lead to a rigid mindset where estimates and commitments are made with the same level of inflexibility as a traditional contract. Instead, Agile teams should recognize the negotiable nature of USs and remain open to adapting them as circumstances warrant. \\ 
\textbf{Valuable}\\ 
The criterion of Value underscores that US must possess inherent worth and significance. A US should be designed in such a way that it delivers tangible value to either the end-users or the stakeholders. The value encapsulated within a US can manifest in various forms, such as improved user experiences, enhanced functionality, increased efficiency, or meeting specific business objectives.

Agile teams should prioritize and select USs that offer real, quantifiable value, as this ensures that the development effort is consistently directed toward outcomes that align with the project's overarching goals and objectives.

The concept of Value serves as a guiding principle that encourages Agile teams to continuously assess and prioritize USs based on their potential to contribute positively to the project's success, ultimately enhancing the overall quality and impact of the software being developed.\\ 
\textbf{Estimable}\\ 
An essential condition for a US to be deemed Estimable is that it must be sufficiently well-defined and clear. Ambiguity or lack of clarity within a US can render it inestimable, meaning that the development team cannot provide a reliable estimate of the effort required for implementation.

Estimable USs facilitate the planning process by enabling the team to make informed decisions about the allocation of resources, timeframes, and priorities. Clear and concise USs ensure that the estimation process is based on a solid foundation of understanding, leading to more accurate project planning and execution. \\  
\textbf{Small}\\ 
The attribute of smallness is a pivotal aspect of the INVEST criteria for USs. It pertains to the size and granularity of individual USs. Large stories, present several challenges in Agile development. They tend to be intricate and challenging to estimate accurately. 

A Complex Story refers to a US that is inherently large and resistant to disaggregation into smaller, more granular stories. Complex stories are a source of concern in Agile development because they can hinder effective planning and may require special consideration and strategies to address. Additionally, they pose difficulties in terms of fitting into single iterations or sprints.\\ 
\textbf{Testable}\\ 
The testable attribute signifies that USs should be structured in a manner that allows for the clear demonstration of whether they meet the customer's expectations. The verification of meeting these expectations is typically accomplished through testing.

An overarching goal in Agile development is to maximize the efficiency and effectiveness of testing processes. To achieve this, Agile teams strive for a high degree of test automation, with a target of attaining a test automation rate exceeding 90\%.

Test automation plays a pivotal role in Agile development by enabling rapid and repeatable testing of software features. Automated tests ensure that the software remains consistent with the desired functionality outlined in the US, thereby reducing the risk of regressions and defects.

INVEST grid in table \ref{tb:invest} can be used as a template when the customer and provider meet to evaluate a US \cite{buglione2013improving}.

The INVEST criteria serve as fundamental guidelines that are partially incorporated into the definition of many existing quality frameworks and requirement development tools in Agile methodologies.\\ \\ 


\newgeometry{margin=2.5cm}

\thispagestyle{empty}


\begin{figure}

\begingroup

\footnotesize
\Rotatebox{90}{%

\begin{tabularx}{25cm}{c  X  X  X  X  X}
 INVEST & \multicolumn{1}{c}{Description} & \multicolumn{1}{c}{0} & \multicolumn{1}{c}{1} & \multicolumn{1}{c}{2} & \multicolumn{1}{c}{3} \\
  &  & \multicolumn{1}{c}{Poor/Absent} & \multicolumn{1}{c}{Fair} & \multicolumn{1}{c}{Good} & \multicolumn{1}{c}{Excellent} \\
\hline
\hline
\\
 I – Independent & User Stories should be as independent as possible & The start of construction of a US is tied to the completion of at least one other US & The completion of a US hinders the start of construction of at least one other US  & The US can contain any constraint, but its release can be constrained by the completion of at least one other US  & The US is fully independent, and it can be realized and released with any constraint \\
 \\
 N – Negotiable & User Stories should be \enquote{open}, reporting any relevant details as much as possible & The US contains enough detail to be a technical specification (Design phase), leaving no room to negotiate any element & The US is written with enough detail to be a functional specification (Analysis phase), leaving no room to negotiate any element & The US is written with informative content defining a User Requirement in a consolidated manner, yet shared between Customer and Provider  & The US is written with the informative content typical of a high-level need, allowing feedback between customer and provider \\
\\
 V – Valuable & User Stories should provide value to end users in terms of the solution & The functional part (F) of the US does not contain all the functionalities requested by the customer & The functional (F) part of the US expresses mostly qualitative (Q) and technical (T) requirements about the system, and needs to be more developed in terms of functional requirements & The functional (F) part of the US expresses mostly the functional requirements requested by the Customer, but also includes qualitative (Q) and technical (T) requirements & The functional (F) part of the US correctly expresses only the functional requirements requested by the customer \\

 \\
 E – Estimable & Each User Story must be able to be estimated in terms of relative size and effort & The US shows only its functional (F) part, filled in by the customer, but without sufficient detail to allow the provider to fill in the Q/T parts & The US shows only its functional (F) part, filled in by the customer, but validated with the provider  & The US has been completed by the provider with respect to Q/T issues, but still needs to be validated jointly with the customer & All the useful parts of the US (F/Q/T) are shown, allowing the effort need to size and estimate it, and validated by both parts \\

 \\
 S – Small & Each User Story should be sufficiently granular, and not defined at too high a level & The US is very large, and cannot be completed within a Sprint & The US is very large, and can be completed within a Sprint, but cannot accommodate the creation/delivery of other US & The size of the US is such that it can be completed within a Sprint, jointly with other US, but it is too small to create overhead about the Testing phase  & The size of the US is such that it can be completed within a Sprint, jointly with other US, ensuring an appropriate balance between development and testing activities \\

 \\
 T – Testable & Each User Story must be formulated in an effort to stress useful details for creating tests & The US does not include tips about Acceptance Tests & The US includes a formal indication of Acceptance Tests, but yet to be completed & The US includes an indication of Acceptance Tests which are complete, but yet to be validated & The US includes an indication of completed and validated Acceptance Tests \\
 \\
 \hline

\end{tabularx}

}%
\begin{TableCaption}
\caption{INVEST Grid \cite{buglione2013improving}}\label{tb:invest}
\end{TableCaption}
\endgroup
\end{figure}
\restoregeometry
\input{Section/USQ_2}